Molecular alignment on graphene surface determines tansport properties of graphene/organic semiconductor transistors

### 2020-04-09 manuscript.tex
Added a paragraph to the end of discussion

>>>>

 The mobility of the second transport channel through OS layer is expected to be lower compared
 to mobility in graphene, due to reduced transfer intergral between molecules due to weak VdW interaction.
 Therefore, we believe that the measured mobility dependence results mainly from the mobility dependence of graphene on the
 charge density, as was theoretically predicted in Ref. \onlinecite{majorana_charge_2016}.
 Their theoretical modeling demonstrate how the electron mobility in graphene drops with charge density.
 In our cast, the charge density is being transfered from OS adlayers.
 However such charge transfer not only increases charge density in graphene, but also pin the Fermi energy and CNP.
 The interplay between these two phenomena is expected to show complex behaviour.
 Nevertheless, our results clearly demonstrate that the first flat-lying OS layer is enough to reduce CNP.
 However, the perpenicular stacking of perylene-like molecules further increases $n_0$ and reduces carrier mobility.
